Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2024-09-19 Manuscript_Nater_etal.qmd
Reduced number of digits to display

  print.out <- list(
    area.name = table$Area[row],
    post.sum = paste0(
      round(table$Median[row], digits = 3), 
      " [",
      round(table$lCI[row], digits = 3),
      ", ",
      round(table$uCI[row], digits = 3),
      "]"
    )
  )
  return(print.out)
}

@@

```{r, echo = FALSE}
DDcorrs <- readRDS("Results/DD_corrCoef.rds")
DD_min_lam <- round(min(subset(DDcorrs, Parameter == "Lambda")$`50%`), digits = 3)
DD_max_lam <- round(max(subset(DDcorrs, Parameter == "Lambda")$`50%`), digits = 3)

VRcorrs <- readRDS("Results/VR_corrCoef.rds")
samCorr_mean <- round(subset(VRcorrs, area == "Overall")[,2:3], digits = 3)
```

@@

```{r, echo = FALSE}
GT <- readRDS("Results/PosteriorSummaries_GenTime_byArea.rds")
GT_R0 <- subset(GT, GT_measure == "Per generation growth rate")
GT_elas <- subset(GT, GT_measure == "Inverse of fecundity elasticity")
medianCorr <- round(cor(GT_R0$Median, GT_elas$Median), digits = 3)

@@

GT_min <- round(GT[minIdx, c("Median", "lCI", "uCI")], digits = 3)
GT_max <- round(GT[maxIdx, c("Median", "lCI", "uCI")], digits = 3)

>>>>

  print.out <- list(
    area.name = table$Area[row],
    post.sum = paste0(
      round(table$Median[row], digits = 2), 
      " [",
      round(table$lCI[row], digits = 2),
      ", ",
      round(table$uCI[row], digits = 2),
      "]"
    )
  )
  return(print.out)
}

@@

```{r, echo = FALSE}
DDcorrs <- readRDS("Results/DD_corrCoef.rds")
DD_min_lam <- round(min(subset(DDcorrs, Parameter == "Lambda")$`50%`), digits = 2)
DD_max_lam <- round(max(subset(DDcorrs, Parameter == "Lambda")$`50%`), digits = 2)

VRcorrs <- readRDS("Results/VR_corrCoef.rds")
samCorr_mean <- round(subset(VRcorrs, area == "Overall")[,2:3], digits = 2)
```

@@

```{r, echo = FALSE}
GT <- readRDS("Results/PosteriorSummaries_GenTime_byArea.rds")
GT_R0 <- subset(GT, GT_measure == "Per generation growth rate")
GT_elas <- subset(GT, GT_measure == "Inverse of fecundity elasticity")
medianCorr <- round(cor(GT_R0$Median, GT_elas$Median), digits = 2)

@@

GT_min <- round(GT[minIdx, c("Median", "lCI", "uCI")], digits = 2)
GT_max <- round(GT[maxIdx, c("Median", "lCI", "uCI")], digits = 2)
